Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-03-28 ms5n17-tlp-mn-180216-001.tex
All the commnets which could be added are added

micro-NMR detectors for flow probes, where the sample container takes the form

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart
The semi-rigid cables (RG 402) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. \cbstart It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
 The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart SMP Connector Receptacle Male Pin is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3. The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\frac{\chi/PPM}{\rho/(g cm^{-3})}$	\\
\hline
PMMA		&-7.609(5)	\\
Copper	&-9.63	\\
FR4	&-1.918(9)		\\
Aluminium	&20.7	\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

\cbstart The double resonance circuit is based on the design shown in \fig{fig:circuit}.\cbend
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger
%sample volumes for some cases.
 The transmission line detector is tuned to the desired proton
Larmor frequency by chip capacitors located at its four corners,
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the
vicinity of 50$\Omega$. A short microstrip
with a specific impedance of 50$\Omega$
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz
could be achieved without $L_1$.
\cbstart
\begin{table}[h]
\centering
\caption{Details of the circuit elements}
\label{tab:circut}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}||}
\hline
Circuit element   & Value	&Part Number\\
\hline
$C_1$, $C_2$ and, $C_8$		&1-23 pf	& NMAM25HV\\
$C_9$	&3-23 pf	& NMNT23-6\\
$C_3$, $C_7$	&4.3 pf		& S111TUE\\
$C_4$	&82 pf	& S111TUE\\
$C_5$, $C^{'}_{5}$	&2.4	& S111TUE\\
$L_3$, $L_7$	 &16.6 nH	& 17NGLB\\
$L_1$	&100 nH	& 4.7\\
$C_6$	&3-23 pf	& NMAJ25HV\\
$C_{20}$  & 2.4 pf		& S111TUE\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=.96\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe.
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
}
\label{fig:circuit}
\end{figure}
\cbend
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks,
Dassault Syst\`{e}mes). Prefabricated profiles made from 6061-T3 aluminium
(Aluminum Warehouse, UK) were used for the mechanical structure of the probe
(base platform, scaffold tubes, sleeve). A few customised precision-machined
parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford,
UK) after providing CAD files. A small number parts were machined in-house
(detector support rods, auxiliary support disks). All electronic components
including semi-rigid transmission lines were purchased from DigiKey Ltd. Cell
cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
(Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
cut to desired size and functionality (holes or channels) using a laser
engraving system  (HPC Laser L3040), and then bonded using the protocol
described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm \cbstart diameter copper wire, \cbend which were soldered to the appropriate pads in
the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian
600 premium shielded 14.1 T magnet. Imaging experiments were performed on Bruker
AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK
and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life
Technologies, USA.

Precision-cut murine liver slices (PCLS) were obtained by first extracting a
tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
thickness were cut from the core using a Krumdieck Tissue slicer, and then
reduced to 3~mm diameter using a smaller punch. The slices were incubated in
well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
for 2 hours before imaging.

\cbstart
\fig{fig:field map} were created through having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms. \fig{fig:1H-nutation} of the water peak in an aqueous solution of 100~mM $^{15}$N-urea. \fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz. The spectrum was acquired with water presaturation at 100~Hz. 32 transients were averaged with a repetition delay of 3~s. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
is shown in \fig{fig:media-spec}.
The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.
The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
of the tissue \fig{fig:tisli}(C) shows a
RARE image using the same parameters, with 8 echos acquired per scan, thus
reducing the acquisition time to 8 minutes. A spin echo image is shown in
\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images
with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
\cbend

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
\caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
(\textsuperscript{13}C frequency at 11.7 T). Probe can be tuned to 2
frequencies at a time, above results were measured in pairs of 600 MHz with 60
MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the frequencies
as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm}
\end{figure}
\cbend
Initially, FR4 PCB material was used for the
detector assembly because of its low cost and easy availability. Inhomogeneities
in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
chamber were constructed from 2 gradient echo (FLASH) images for both FR4
and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
brightness of each pixel is proportional to the sum of the magnitude of the two
images, whereas the colour encode the phase difference between them. The full
colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.

B$_{0}$ field map of RO3035 PCB material clearly show better B$_{0}$ field homogeneity compare to FR4. To avoid the inhomogeneities in FR4 and therefore to achieve better resolution,
detectors were made from RO3035. While RO3035 provides better
resolution, it is more expensive and takes longer to obtain compared to FR4. It
therefore makes sense to first prototype new detector designs in FR4, and only
use the more expensive RO3035 once the design has been validated.

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}
\cbend

The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz~\fig{fig:1H-nutation}. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec}
\end{figure*}

\fig{fig:lineshape} shows the spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported
by Finch et al. at 300~MHz. While the residual cause of broadening is still
under investigation, we have reason to suspect imperfections in the fabrications
of the PMMA microfluidic devices to play a major role. Efforts to mitigate these
and to achieve more highly resolved proton spectra are currently underway in our
laboratory and will be reported at a later occasion.  The limit of detection
$nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ of
protons at 600 MHz, slightly better than the value reported for a smaller
detector by Finch et al.~\cite{gream_2016}.

Even though the resolution of the proton spectra still needs to be improved, it
is sufficient to analyse complex mixtures. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) shown in \fig{fig:media-spec} demonstrates the suitability of this
probe for metabolomic studies of microfluidic cultures of cells, tissues, and
small organisms.

\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the
current setup. The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum of $^{13}$C-glucose and the right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum of $^{15}$N-ubiquitin (17 $\mu$g). All
expected cross peaks are present in the spectrum. The ability to obtain
meaningful  \textsuperscript{15}N-\textsuperscript{1}H correlation spectra from
such small samples could prove very useful in the context of proteins that are
difficult to express and therefore only available in small quantities. The
integration of protein NMR and microfluidic technology also opens new
possibilities for high-throughput kinetics and binding studies.

>>>>

micro-NMR detectors for flow probes\cbstart~\cite{bas-shim,Montinaro-2018,chen2017high,oosthoek2017continuous,bart2009microfluidic,bart2009optimization,massin2003planar}\cbend, where the sample container takes the form

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart
The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. \cbstart It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
 The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart SMP Connector Receptacle Male Pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}). The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}. \cbstart Magnetic susceptibility value of PMMA and other materials in given in table~\ref{tab:susceptibility}\cbend
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\chi$/ppm	\\
\hline
PMMA		&-9.054	\\
Copper	&-9.63	\\
FR4	&-3.743		\\
Aluminium	&20.7	\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

\cbstart The double resonance circuit is based on the design shown in \fig{fig:circuit}.\cbend
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger
%sample volumes for some cases.
 The transmission line detector is tuned to the desired proton
Larmor frequency by chip capacitors ($C_{20}$) located at its four corners,
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the
vicinity of 50$\Omega$. A short microstrip
with a specific impedance of 50$\Omega$
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz
could be achieved without $L_1$. \cbstart Details of all the circuit elements are given in table~\ref{tab:circuit}.
\begin{table}[h]
\centering
\caption{Details of the circuit elements to tune the probe at 600 MHz and 60 MHz.}
\label{tab:circuit}
\begin{tabular}{||p{.3\linewidth}|p{.2\linewidth}|p{.3\linewidth}||}
\hline
Circuit element   & Value	&Manufacturer Part Number	\\
\hline
$C_1$, $C_2$ and, $C_8$		&1-23 pF	& NMAM25HV\\
$C_9$	&3-23 pF	& NMNT23-6\\
$C_6$	&3-23 pF	& NMAJ25HV\\
$C_{20}$  & 2.4 pF		& S111TUE\\
$C_3$, $C_7$	&4.3 pF		& S111TUE\\
$C_4$	&82 pF	& S111TUE\\
$C_5$, $C^{'}_{5}$	&2.4 pF	& S111TUE\\
$L_1$	&111 nH	& 1010VS-111ME\\
$L_3$, $L_7$	 &16.6 nH	& 17NGLB\\
$J_1$, $J_2$ & -&0734153591\\
$J_3$, $J_4$ & -&SMP-MSLD-PCT-5\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. The background colour relates the different circuit elements on different PCBs. The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation. The front side of the TMPCB 7 is shown in vertical orientation. Trimmer capacitor $C_6$ is placed on the back side of PCB plane 5. The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white. An insulating solder mask layer over the copper layer prevents accidental short-circuiting. 
}
\label{fig:circuit}
\end{figure}
\cbend
\section{Materials and Methods}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks,
Dassault Syst\`{e}mes). Prefabricated profiles made from 6061-T3 aluminium
(Aluminum Warehouse, UK) were used for the mechanical structure of the probe
(base platform, scaffold tubes, sleeve). A few customised precision-machined
parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford,
UK) after providing CAD files. A small number parts were machined in-house
(detector support rods, auxiliary support disks). All electronic components
including semi-rigid transmission lines were purchased from DigiKey Ltd \cbstart and Farnell element14, UK. Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
(Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
cut to desired size and functionality (holes or channels) using a laser
engraving system  (HPC Laser L3040), and then bonded using the protocol
described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm \cbstart diameter copper wire bought from RS components, UK, \cbend which were soldered to the appropriate pads in the four corners of the detector structure.

\cbstart
\subsection{Details of NMR and MRI measurements}
NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet. Field maps in the \fig{fig:field map} were created by gradient echo (FLASH) pulse sequence with echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms on a sample of 130 mM  sodium acetate dissolved in H$_2$O. The peak shown in the \fig{fig:1H-nutation} is of H$_2$O in an aqueous solution of 100~mM $^{15}$N-urea. \fig{fig:lineshape} shows proton spectrum of the acetate resonance from 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O. The spectrum was recorded after presturating the water signal with rf-field of 100~Hz. 32 transients were averaged with a repetition delay of 3~s. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) cell growth medium in \fig{fig:media-spec} was acquired with 256 scans in 20 mins.
The left panel of \fig{fig:HSQC} shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.

For MRI experiments precision-cut murine liver slices (PCLS) were obtained by first extracting a
tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
thickness were cut from the core using a Krumdieck Tissue slicer, and then
reduced to 3~mm diameter using a smaller punch. The slices were incubated in
well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
for 2 hours before imaging. Imaging experiments were performed on Bruker
AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet. The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness of the tissue \fig{fig:tisli}(C) shows a
RARE image using the same parameters, with 8 echos acquired per scan, thus
reducing the acquisition time to 8 minutes. A spin echo image is shown in
\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images
with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
\cbend

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
\caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
(\textsuperscript{13}C frequency at 11.7 T). Probe can be tuned to 2
frequencies at a time, above results were measured in pairs of 600 MHz with 60
MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the frequencies
as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm}
\end{figure}
\cbend
Initially, FR4 PCB material was used for the
detector assembly because of its low cost and easy availability. Inhomogeneities
in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
be seen as fringes in~\fig{fig:field map} (A). \cbdelete B$_{0}$ field maps of the sample
chamber were constructed from 2 gradient echo (FLASH) images for both FR4
and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
brightness of each pixel is proportional to the sum of the magnitude of the two
images, whereas the colour encode the phase difference between them. The full
colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.
\cbdelete
B$_{0}$ field map of RO3035 PCB material clearly show better B$_{0}$ field homogeneity compare to FR4. To avoid the inhomogeneities in FR4 and therefore to achieve better resolution,
detectors were made from RO3035. While RO3035 provides better
resolution, it is more expensive and takes longer to obtain compared to FR4. It
therefore makes sense to first prototype new detector designs in FR4, and only
use the more expensive RO3035 once the design has been validated.

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}
\cbend
\cbdelete 
The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz shown in~\fig{fig:1H-nutation}. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec}
\end{figure}
\cbdelete 
\fig{fig:lineshape} shows the proton spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported
by Finch et al. at 300~MHz. While the residual cause of broadening is still
under investigation, we have reason to suspect imperfections in the fabrications
of the PMMA microfluidic devices to play a major role. Efforts to mitigate these
and to achieve more highly resolved proton spectra are currently underway in our
laboratory and will be reported at a later occasion.  The limit of detection
$nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ of
protons at 600 MHz, slightly better than the value reported for a smaller
detector by Finch et al.~\cite{gream_2016}.

Even though the resolution of the proton spectra still needs to be improved, it
is sufficient to analyse complex mixtures. \cbdelete The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) shown in \fig{fig:media-spec} demonstrates the suitability of this
probe for metabolomic studies of microfluidic cultures of cells, tissues, and
small organisms.
\cbdelete 
\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the
current setup. The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum of $^{13}$C-glucose and the right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum of $^{15}$N-ubiquitin (17 $\mu$g). All
expected cross peaks are present in the spectrum. The ability to obtain
meaningful  \textsuperscript{15}N-\textsuperscript{1}H correlation spectra from
such small samples could prove very useful in the context of proteins that are
difficult to express and therefore only available in small quantities. The
integration of protein NMR and microfluidic technology also opens new
possibilities for high-throughput kinetics and binding studies.
